MS&E 226: Project Part 1 Code

### 2024-12-02 MS&E 226_Project Part 2_Code.Rmd
comments

set.seed(123) # Setting seed for reproducibility
```

# 2: Data Pre-processing

@@

# 3: Hold Out Set

@@

# 5: Data Exploration

## Correlations

@@

## Subgroups in data

@@

# 6: Regression

## Data Transformations

@@

## Baseline Model

@@

## Cross Validation setup

@@

## Model 1: Ridge Regression

@@

## Model 2: Lasso Regression

@@

## Model 3: Random Forest

@@

rf_model_rmse <- min(rf_model$results$RMSE)
cat(paste("Random Forest RMSE:", rf_model_rmse, "\n"))
```

# 7: Classification

## Data Cleaning

@@

## Classifier 1: K-NN

@@

## Classifier 2: Logistic Regression with Feature Selection

@@

## Classifier 3: Decision Tree

@@

## Comparing Classifiers

@@

## 1: Prediction on the holdout set

@@

#### a)

@@

## 2: Inference

#### (a)
```{r 2a}
# Extract the final Ridge model using the best lambda
final_ridge_model <- ridge_model$finalModel

@@

#### (b)
```{r}
# Select a subset of covariates
subset_column_names <- c(  "Demand.Summer.Peak", "Demand.Winter.Peak", "Sources.Generation", "Utility.Region", "Max.Revenue.Sector", "Revenue.Total", "Utility.Type")

@@

```
```{r}
# Get the coefficients for the best model at the selected lambda
best_lambda <- ridge_model$bestTune$lambda
best_model_coeffs <- coef(ridge_model$finalModel, s = best_lambda)

@@

#### (c)

@@

```{r 2d bootstrap Ridge}

>>>>

set.seed(123) # Setting seed for reproducibility
```
#Projetc Part 1

## 2. Data Pre-processing

@@

## 3. Hold Out Set

@@

## 5. Data Exploration

### Correlations

@@

### Subgroups in data

@@

## 6. Regression

### Data Transformations

@@

### Baseline Model

@@

### Cross Validation setup

@@

### Model 1: Ridge Regression

@@

### Model 2: Lasso Regression

@@

### Model 3: Random Forest

@@

rf_model_rmse <- min(rf_model$results$RMSE)
cat(paste("Random Forest RMSE:", rf_model_rmse, "\n"))
```
## 7. Classification

### Data Cleaning

@@

### Classifier 1: K-NN

@@

### Classifier 2: Logistic Regression with Feature Selection

@@

### Classifier 3: Decision Tree

@@

### Comparing Classifiers

@@

## 1. Prediction on the holdout set

@@

@@

## 2. Inference

### Statistically significant Coeficients
```{r 2a}
# Extract the final Ridge model using the best lambda
final_ridge_model <- ridge_model$finalModel

@@

### Subset of covariates
```{r}
# Select a subset of covariates
subset_column_names <- c(  "Demand.Summer.Peak", "Demand.Winter.Peak", "Sources.Generation", "Utility.Region", "Max.Revenue.Sector", "Revenue.Total", "Utility.Type")

@@

```{r}
# Get the coefficients for the best model at the selected lambda
best_lambda <- ridge_model$bestTune$lambda
best_model_coeffs <- coef(ridge_model$finalModel, s = best_lambda)

@@

### Fit on Holdout set

@@

### Bootstrap
```{r 2d bootstrap Ridge}
